The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-10-18 paper.qmd
separate and save questionable code chunks (api or depreciated)

```{r}
#| eval: false
#| echo: false
# Get map data: do this once and save
my_map_data <- get_urbn_map("counties", sf = TRUE) |>
  filter(state_name=="Iowa")
save(my_map_data, file="data/my_map_data.rda")
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-data
#| fig-cap: "The first 5 observations of the data used for the spatial uncertainty examples along with the boundaries of each county. The map boundaries are the Iowa county boundaries, however the 'temperature' data is not representative of the average temperature in Iowa. The temperature and standard error represent the average of the daily high temperature and the standard error of that average respectively."
#| fig-subcap: 
#|   - "Data Table"
#|   - "Map Boundaries"
#| layout-nrow: 1
#| cap-location: "bottom"
load("data/my_map_data.rda")

@@

# Get map data
my_map_data <- get_urbn_map("counties", sf = TRUE) |>
  filter(state_name=="Iowa")
centroids <- as_tibble(gCentroid(as(my_map_data$geometry, "Spatial"), byid = TRUE))
my_map_data$cent_long <- centroids$x
my_map_data$cent_lat <- centroids$y
n <- dim(my_map_data)[1]

@@

# Pixel Map

# Low variance map
my_map_data_a <- my_map_data |>
  filter(variance_class == "lowvar") |>
  mutate(my_id = seq(n),
         error = variance)

@@

# Display plots and palettes
p4a
p4b
show_pal(longpal, ncol=13, borders="white", myxlab = "Temperature", breaks = 19:32, textnudge = c(0.2, 0.1, 0,0,0,0,0,0,0,0,0,0,-0.1,-0.2), xlabx= 6.5, xlaby=-2.2)
```

>>>>

```{r}
#| eval: false
#| echo: false
# Get map data: do this once and save
my_map_data <- get_urbn_map("counties", sf = TRUE) |>
  filter(state_name=="Iowa")
save(my_map_data, file="data/iowa_map.rda")
```

```{r}
#| eval: false
#| echo: false
# Get centroid because rgeos is depreciated
load("data/iowa_map.rda")
centroids <- as_tibble(gCentroid(as(my_map_data$geometry, "Spatial"), byid = TRUE))
my_map_data$cent_long <- centroids$x
my_map_data$cent_lat <- centroids$y
save(my_map_data, file="data/my_map_data.rda")
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-data
#| fig-cap: "The first 5 observations of the data used for the spatial uncertainty examples along with the boundaries of each county. The map boundaries are the Iowa county boundaries, however the 'temperature' data is not representative of the average temperature in Iowa. The temperature and standard error represent the average of the daily high temperature and the standard error of that average respectively."
#| fig-subcap: 
#|   - "Data Table"
#|   - "Map Boundaries"
#| layout-nrow: 1
#| cap-location: "bottom"

# get data
load("data/my_map_data.rda")

@@

# data dimension for sampling
n <- dim(my_map_data)[1]

@@

```{r}
#| eval: false
#| echo: false
# Make + save pixel map (in case of depreciation)
# Low variance map
my_map_data_a <- my_map_data |>
  filter(variance_class == "lowvar") |>
  mutate(my_id = seq(n),
         error = variance)

@@

save(p4a, file="data/p4a.rda")
save(p4b, file="data/p4b.rda")
```

# load pixel maps
load("data/p4a.rda")
load("data/p4b.rda")
# Display plots and palettes
p4a
p4b
show_pal(longpal, ncol=13, borders="white", myxlab = "Temperature", breaks = 19:32, textnudge = c(0.2, 0.1, 0,0,0,0,0,0,0,0,0,0,-0.1,-0.2), xlabx= 6.5, xlaby=-2.2)
```
